Capstone Movielens Report

### 2025-12-07 reports/capstone-movielens.site/02.5.UME-model.Rmd
Fix for fine-tuning-related sections of the report (UME, UMGE, UMGYE models).

\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
For this purpose, we will use the helper function [model.tune.param_range](#func.model.tune.param_range), passing the  function (already mentioned above in the [UME Model Regularization: *Pre-configuration*] section) as the value of its argument [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value).

\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

@@

::: {.noteblock data-latex=""}
Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions]) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that the deviations from the mean of $y$ are used to plot, rather than the $y$ values themselves.
:::

>>>>

@@

::: {.noteblock data-latex=""}
Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions]) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves.
:::

### 2025-12-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Fix for fine-tuning-related sections of the report (UME, UMGE, UMGYE models).

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section can be found in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L867) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
:::

@@

Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.

@@

UMGYE.loop_starter <- c(endpoints["start"], 
                        endpoints["end"], 
                        8)
UMGYE.loop_starter
#> [1]

cache.base_name <- "UMGYE.rglr.fine-tuning"

UMGYE.rglr.fine_tune.results <- 
  model.tune.param_range(UMGYE.loop_starter,
                         UMGYE.rglr.fine_tune.cache.path,
                         cache.base_name,
                         regularize.test_lambda.UMGY_effect.cv)
```
```{r}
str(UMGYE.rglr.fine_tune.results)
UMGYE.rglr.fine_tune.results$best_result
```

::: {.noteblock data-latex=""}
Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions] to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
:::

@@

::: {.noteblock data-latex=""}
We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions], which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
:::

>>>>

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization: Fine-tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1281) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1281) script on _GitHub_.
:::

@@

@@

UMGYE.loop_starter <- c(endpoints["start"], 
                        endpoints["end"], 
                        8)
```

::: {.noteblock data-latex=""}
The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) of [Appendix A: Support Functions].
:::

```{r}
UMGYE.loop_starter
UMGYE.rglr.fine_tune.cache.path
```
```{r, eval=FALSE}
cache.base_name <- "UMGYE.rglr.fine-tuning"

UMGYE.rglr.fine_tune.results <- 
  model.tune.param_range(UMGYE.loop_starter,
                         UMGYE.rglr.fine_tune.cache.path,
                         cache.base_name,
                         regularize.test_lambda.UMGY_effect.cv)

UMGYE.rglr.fine_tune.RMSE.best <- UMGYE.rglr.fine_tune.results$best_result["best_RMSE"]
```

::: {.noteblock data-latex=""}
The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

```{r, echo=FALSE}
writeLines("*** Fine-tuning results object data structure ***")
```
```{r}
str(UMGYE.rglr.fine_tune.results)
```
```{r, echo=FALSE}
writeLines("*** Fine-tuning: best results ***")
```
```{r}
UMGYE.rglr.fine_tune.results$best_result
UMGYE.rglr.fine_tune.RMSE.best
```

@@

::: {.noteblock data-latex=""}
Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions]) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves.
:::

### 2025-12-07 reports/capstone-movielens.site/05.appendix.Rmd
Fix for fine-tuning-related sections of the report (UME, UMGE, UMGYE models).

:::
::: { #func.data.plot.args.normalize .sidebar }
  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.

>>>>

:::
::: { #func.data.plot.args.normalize .sidebar }
- **normalize = FALSE:** If `TRUE`, deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves. Otherwise, the $y$ values are used.
